(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2015-04-29 ms/ms.Rnw
worked on Discussion

The observation that populations are locally adapted to their environment is old and well-documented in many species. New frontiers in local adaptation research aim at a general understanding of why local adaptation sometimes suceeds and other times fails, why certain traits respond to selection whereas others are constrained, and what are the important environmental drivers of local adaptation [CITES such as Kawecki]. Understanding why and how populations adapt to different environments is especially significant for predicting how species' ranges will shift under climate change. In this study, we found evidence for one of two common signature of local adaptation, pointing to both phenotypic lability and constraint. ...

<- add to above: 1. How does local adaptation occur? It's complex (gene flow, shape of tradeoffs, demography) and although there is abundant evidence for local adaptaiton, we do not a general sense for when local adaptation succeeds or fails. For this, we need a system in which there are axes of variation and constraint, traits with known physiological function?, and selective agents

@@

@@

4. Why does local adaptation fail? concave, high gene flow, demography. Qualify that our metrics of plasticity are coarse, but at least suggest that GxE is much weaker than G for the environmental gradients evaluated here.

>>>>

The observation that populations are locally adapted to their environment is old and well-documented in many species. New frontiers in local adaptation research seek a general understanding of why local adaptation often suceeds but sometimes fails, why certain traits respond to selection whereas others are constrained, and what environmental drivers are most important [CITES such as Kawecki]. Understanding why and how populations have adapted to different environments in the past is especially significant npw because it the scientific basis for predicting how species' ranges will shift under climate change [CITES, Catullo_etal_2015]. In this study, we found evidence for one of two common signature of local adaptation, pointing to both phenotypic lability and constraint related to local adaptation. In particular, our data suggest that photosynthesis and intrinsic growth rate vary among populations, whereas the fundamental abiotic niche is more conserved, and that climatic variation may be a more important selective agent than the average. Next, we tie these results into the broader threads of evolutionary theory in order to figure out what factors best explain our data.

As long as environments vary and there exists genetic variation in fitness, why shouldn't local adaptation suceed? Evolutionary theory indicates that the shape of fitness tradeoffs, demography, and gene flow can constrain local adaptation. In \textit{M. cardinalis} we found substantial genetic variation among populations along a phenotypic axis from fast to slow growth (Fig.~\ref{fig:Fig_PC1vLat}). Th... fitness tradeoffs are not too strong, demographic symmetry, and attenuation of gene flow.

@@

Although evolutionary theory ... But what we really need to understand is why certain types of traits are repeatedly targets of natural selection, whereas other traits are constrained.

@@

(also 4.) Another possibility we could have seen is that southern populations, which appear to experience more frequent drought years, could have evolved the ability to tolerate drought better than northern populations, thereby expanding the fundamental niche of the species as a whole. We found no evidence for this; all populations responded to drought and temperature treatments similarly (Table~\ref{table:Table_AnovaSummary}). However, evolution of the fundamental niche may be constrained by a combination of strong fitness tradeoffs, demographic asymmetry, and gene flow. Riparian habitats are highly heterogeneous at small spatial scales. Plants in the stream never have to tolerate drought whereas plants only a few meters away may experience extreme drought if there is little direct precipitation during the growing season, as in Meditteranean climates of Western North America. But alleles that confer greater drought tolerance may be quite costly in well-watered soils, leading to strong fitness tradeoffs. Such tradeoffs promote specialization to one soil type or another, thereby inhibiting the evolution of broad environmental tolerance within a population. Demography and gene flow may reinforce niche conservatism. A new mutant with increased drought tolerance that can survive at the margin of a population. But if . Finally, gene flow, which is generally high among \textit{M. cardinalis} populations within the same ecoregion \citep{Paul_etal_2015}, will thwart local adaptation and reinforce specialization. Spatial grain of the environment, demographic asymmetry, and gene flow conspire to thwart local adaptation via altered fundamental niche.
4. Why does local adaptation fail? concave, high gene flow, demography. Qualify that our metrics of plasticity are coarse, but at least suggest that GxE is much weaker than G for the environmental gradients evaluated here.

highly connected by gene flow, outcrossing (self-compatible but strongly herkogamous)

? It's complex (gene flow, shape of tradeoffs, demography) and although there is abundant evidence for local adaptaiton, we do not a general sense for when local adaptation succeeds or fails. For this, we need a system in which there are axes of variation and constraint, traits with known physiological function?, and selective agents
